### 2023-01-13 code/plots.Rmd
plots of fixed action

---
---

@@

```{r}
ppo <- read_csv("../data/PPO.csv.gz")
```

```{r}
ppo |> 
  mutate(pop = (sp1+1)/2, 
         escapement = pop - action * pop) |> 
  ggplot(aes(t, escapement, group=rep)) + geom_line() + ylim(0,1)
```

@@

@@

>>>>

---
output: github_document
---

This notebook generates plots from the `.csv` results produced by the corresponding python scripts.  We compare policies across constant effort (MSY-like policies), constant escapement, and the RL agent (PPO).

@@

# Constant Effort

@@

# Constant Escapement

@@

# PPO Agent

```{r}
ppo <- read_csv("../data/PPO-long.csv.gz")
```

```{r}
ppo |> ggplot(aes(t, sp1, group=rep)) + geom_line()

ppo |> ggplot(aes(t, reward, group=rep)) + geom_line()

ppo |> 
  mutate(pop = (sp1+1), 
         escapement = pop - action * pop) |> 
  ggplot(aes(t, escapement, group=rep)) + geom_line() + ylim(0,1)

ppo |> 
  mutate(effort = pmax(1 - action / sp1, 0)) |>
  pivot_longer(c("sp1", "sp2", "sp3"), names_to = "species", values_to = "abundance") |>
  ggplot(aes(t, abundance, group = interaction(species, rep), col=species)) +
  geom_line(alpha=0.8)

```{r}
ppo |> filter(t == max(t)) |> pull(reward) |> mean()
ppo |> filter(t == max(t)) |> pull(reward) |> sd()
